Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-23 ICLR25/experiments.tex
exp

Notice that several other verifiers were already reported \cite{crown} on these same DNNs, with defavorable comparison towards $\alpha,\beta$-CROWN (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc). Further, we reported accuracy of complete verifiers, NNenum \cite{nnenum}, Marabou \cite{Marabou, Marabou2}, respectively 4th, 3rd 
of the last VNNcomp'24 \cite{VNNcomp24}, as well as full MILP \cite{MILP} in Table \ref{table_complete}, showing that these verifiers are not competitive on hard instances either, even on the smallest hard DNN. Concerning MnBAB \cite{ferrari2022complete}, it compares slightly defavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv \cite{ferrari2022complete}, and we also run it for the MNIST DNNs, and it was slightly slower and less accurate than $\alpha,\beta$-CROWN at several time-out settings. 
Last, Pyrat code is not open source, which made running it impossible.

>>>>

Notice that results for several other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported on these DNNs \cite{crown}, with defavorable comparison vs $\alpha,\beta$-CROWN. Further, we reported accuracy of complete verifiers, NNenum \cite{nnenum}, Marabou \cite{Marabou, Marabou2}, respectively 4th, 3rd 
of the last VNNcomp'24 \cite{VNNcomp24}, as well as full MILP \cite{MILP} in Table \ref{table_complete}, showing that these verifiers are not competitive on hard instances either, even on the smallest hard DNN. Concerning MnBAB \cite{ferrari2022complete}, it compares slightly defavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv \cite{ferrari2022complete}, and we also run it for the MNIST DNNs, and it was slightly slower and less accurate than $\alpha,\beta$-CROWN at several time-out settings. 
Last, Pyrat code (2sd in the latest VNNComp) is not open source, which made running it impossible.
